Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-28 datapaper.tex
xm's first edits

\institute{Jeffrey A Cruz $\cdot$ Jin Chen$\cdot$ David M Kramer \at
              Department of Energy Plant Research Laboratory, Michigan State University, East Lansing, MI 48824, USA  \\
		E-mail: \{cruzj,jinchen,kramerd8\}@msu.edu		
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Xi Yin$\cdot$ Xiaoming Liu (\Letter)\at
              Department of Computer Science and Engineering, Michigan State University,  East Lansing, MI 48824, USA  \\
		E-mail: \{yinxi1,liuxm\}@cse.msu.edu
                      %  \\
              \and
           Saif Imran$\cdot$Daniel D Morris \at
              Department of Electrical and Computer Engineering, Michigan State University,
              East Lansing, MI 48824, USA\\  
		E-mail: \{imransai,dmorris\}@msu.edu
}

>>>>

\institute{Jeffrey A Cruz $\cdot$ Jin Chen $\cdot$ David M Kramer \at
              Department of Energy Plant Research Laboratory, Michigan State University, East Lansing, MI 48824, USA  \\
		E-mail: \{cruzj,jinchen,kramerd8\}@msu.edu		
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Xi Yin $\cdot$ Xiaoming Liu (\Letter)\at
              Department of Computer Science and Engineering, Michigan State University,  East Lansing, MI 48824, USA  \\
		E-mail: \{yinxi1,liuxm\}@cse.msu.edu
                      %  \\
              \and
           Saif Imran $\cdot$ Daniel D Morris \at
              Department of Electrical and Computer Engineering, Michigan State University,
              East Lansing, MI 48824, USA\\  
		E-mail: \{imransai,dmorris\}@msu.edu
}
